\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/proposta/prop.tex
beamtime requested

\begin{table}[H]
\centering
\begin{tabular}{|w{0.4\linewidth}|w{0.3\linewidth}|w{0.15\linewidth}|}
\hline
Phase & Date & Duration \\ \hline
Theoretical Background, Planning and Lab Overview & 30/11/2023 9h30 & 4h \\ \hline
Experiment & 7/12/2023 8h00 & 8h \\ \hline
Results Discussion & ?? 9h30 & 4h \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{|w{0.4\linewidth}|w{0.3\linewidth}|w{0.15\linewidth}|}
\hline
Phase & Date & Duration \\ \hline
Theoretical Background, Planning and Lab Overview & 30/11/2023 9h30 & 4h \\ \hline
Experiment & 7/12/2023 8h00 & 8h \\ \hline
Results Discussion & To be arranged & 4h \\ \hline
\end{tabular}
\end{table}
